---
title: "R Notebook"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---

___13. This question should be answered using the Weekly data set, which is part of the ISLR package. This data is similar in nature to the Smarket data from this chapter's lab, except that it contains 1,089 weekly returns for 21 years, from the beginning of 1990 to the end of 2010.___
```{r}
library(ISLR)
```
```{r}
head(Weekly)
```

a. Produce some numerical and graphical summaries of the Weekly data. Do there appear to be any patterns?
```{r}
summary(Weekly)
```
```{r}
pairs(Weekly)
```
```{r}
cor(Weekly[, -9])
```
There seems to be a correlation between year and volume. There are no other noticeable patterns.

```{r}
plot(Weekly$Volume, ylab = "Shares traded (in billions)")
```

b. Use the full data set to perform a logistic regression with Direction as the response and the five lag variables plus Volume as predictors. Use the summary function to print the results. Do any of the predictors appear to be statistically significant? If so, which ones?
```{r}
attach(Weekly)
glm.fit = glm(Direction ~ Lag1 + Lag2 + Lag3 + Lag4 + Lag5 + Volume, data = Weekly, 
    family = binomial)
summary(glm.fit)
```
With a Pr(>|z|) = 3%, Lag 2 seems to have some statistical significance.

c. Compute the confusion matrix and overall fraction of correct predictions. Explain what the confusion matrix is telling you about the types of mistakes made by logistic regression.
```{r}
glm.probs = predict(glm.fit, type = "response")
glm.pred = rep("Down", length(glm.probs))
glm.pred[glm.probs > 0.5] = "Up"
table(glm.pred, Direction)
```
```{r}
mean(glm.pred == Weekly$Direction)
```
The percentage of accurate predictions is (54 + 557)/(54 + 557 + 48 + 430) = 56.1%. 557/(557+48) = 92.1 percent of the time the logistic regression is accurate during market upswings. When the market rises, the logistic regression is frequently off by 11.2 percent, or 54/(430+54) weeks.

d. Now fit the logistic regression model using a training data period from 1990 to 2008, with Lag2 as the only predictor. Compute the confusion matrix and the overall fraction of correct predictions for the held out data (that is, the data from 2009 and 2010).
```{r}
train = (Year < 2009)
Weekly.0910 = Weekly[!train, ]
glm.fit = glm(Direction ~ Lag2, data = Weekly, family = binomial, subset = train)
glm.probs = predict(glm.fit, Weekly.0910, type = "response")
glm.pred = rep("Down", length(glm.probs))
glm.pred[glm.probs > 0.5] = "Up"
Direction.0910 = Direction[!train]
table(glm.pred, Direction.0910)
```
```{r}
mean(glm.pred == Direction.0910)
```
e. Repeat (d) using LDA.
```{r}
library(MASS)
lda.fit = lda(Direction ~ Lag2, data = Weekly, subset = train)
lda.pred = predict(lda.fit, Weekly.0910)
table(lda.pred$class, Direction.0910)
```
```{r}
mean(lda.pred$class == Direction.0910)
```

f. Repeat (d) using QDA. 
```{r}
qda.fit = qda(Direction ~ Lag2, data = Weekly, subset = train)
qda.class = predict(qda.fit, Weekly.0910)$class
table(qda.class, Direction.0910)
```
```{r}
mean(qda.class == Direction.0910)
```

g. Repeat (d) using KNN with K = 1. 
```{r}
library(class)
train.X = as.matrix(Lag2[train])
test.X = as.matrix(Lag2[!train])
train.Direction = Direction[train]
set.seed(1)
knn.pred = knn(train.X, test.X, train.Direction, k = 1)
table(knn.pred, Direction.0910)
```
```{r}
mean(knn.pred == Direction.0910)
```

h) Repeat (d) using naive Bayes. 

i. Which of these methods appears to provide the best results on this data?

Logistic regression and LDA methods provide similar test error rates.

j. Experiment with different combinations of predictors, including possible transformations and interactions, for each of the methods. Report the variables, method, and associated confusion matrix that appears to provide the best results on the held out data. Note that you should also experiment with values for K in the KNN classifier.
```{r}
# Logistic regression with Lag2:Lag1
glm.fit = glm(Direction ~ Lag2:Lag1, data = Weekly, family = binomial, subset = train)
glm.probs = predict(glm.fit, Weekly.0910, type = "response")
glm.pred = rep("Down", length(glm.probs))
glm.pred[glm.probs > 0.5] = "Up"
Direction.0910 = Direction[!train]
table(glm.pred, Direction.0910)
```
```{r}
mean(glm.pred == Direction.0910)
```
```{r}
# LDA with Lag2 interaction with Lag1
lda.fit = lda(Direction ~ Lag2:Lag1, data = Weekly, subset = train)
lda.pred = predict(lda.fit, Weekly.0910)
mean(lda.pred$class == Direction.0910)
```
```{r}
# QDA with sqrt(abs(Lag2))
qda.fit = qda(Direction ~ Lag2 + sqrt(abs(Lag2)), data = Weekly, subset = train)
qda.class = predict(qda.fit, Weekly.0910)$class
table(qda.class, Direction.0910)
```
```{r}
mean(qda.class == Direction.0910)
```
```{r}
# KNN k =10
knn.pred = knn(train.X, test.X, train.Direction, k = 10)
table(knn.pred, Direction.0910)
```
```{r}
mean(knn.pred == Direction.0910)
```
```{r}

# KNN k = 100
knn.pred = knn(train.X, test.X, train.Direction, k = 100)
table(knn.pred, Direction.0910)
```
```{r}
mean(knn.pred == Direction.0910)
```



